Notes 3-18-19

### 2021-05-03 notes/el_salvador_analysis_1.Rmd
finished small P analysis

- After data cleaning, my ER dataset has 1323 records, while the paper says there should be 1324. 
- The paper has a Bayes estimate with 187 links, but my implementation (with `BRL`) finds 178. This might be because the paper detects adjecent municipalities, while I do not
- Distribution of $m$ parameters for given name substantially different from whats in the paper.

@@

- Within the Sadinle framework, it is typical that Gibbs iterations have more matches than the eventualy Bayes estimate. This is because many of the matches are due to randomness, and they only make it through to the Bayes estimate if that same matching occurs consistently 50% of the time. In Sadinle's paper, the overlap has a mean of 241, and a 90% credible interval of [227, 256], but a Bayes estimate of only 187.

- Severe overmatching within the Gibbs iterations can possibly lead to biased postiors for the $m$ parameters. There is an interesting conversation to be had here. When Enamorado compared `fastlink` to `BRL`, he notes that the first estimate under `fastlink` has way too many matches, but that `fastlink` produces similar results to `BRL` after resolving all the matches that violate one-to-one. While this is true, the overmatching within his EM algorithm lead to biases in the $m$ parameters, and these can not be cleaned up posthoc. In the Sadinle paper, he notes that the FS method leads to nonsensicle estimates of the $m$ parameters, and I believe it is for this reason.

@@

## Good News: Less Patterns Less Time

@@

I think its nice that it demonstrates the influence of the $P$ patterns, but I'm not sure if thats enough. Let me know your thoughts on this!

>>>>

- After data cleaning, my ER dataset has 1323 records, while the paper says there should be 1324. 
- The paper has a Bayes estimate with 187 links, but my implementation (with `BRL`) finds 178. This might be because the paper detects adjacent municipalities, while I do not
- Distribution of $m$ parameters for given name substantially different from whats in the paper.

@@

- Within the Sadinle framework, it is typical that Gibbs iterations have more matches than the eventual Bayes estimate. This is because many of the matches are due to randomness, and they only make it through to the Bayes estimate if that same matching occurs consistently 50% of the time. In Sadinle's paper, the overlap has a mean of 241, and a 90% credible interval of [227, 256], but a Bayes estimate of only 187.

- Severe overmatching within the Gibbs iterations can possibly lead to biased posteriors for the $m$ parameters. There is an interesting conversation to be had here. When Enamorado compared `fastlink` to `BRL`, he notes that the first estimate under `fastlink` has way too many matches, but that `fastlink` produces similar results to `BRL` after resolving all the matches that violate one-to-one. While this is true, the overmatching within his EM algorithm lead to biases in the $m$ parameters, and these can not be cleaned up posthoc. In the Sadinle paper, he notes that the FS method leads to nonsensical estimates of the $m$ parameters, and I believe it is for this reason.

@@

## Good News: Less Patterns Less Problems

I reran everything with only 3 levels for first name, last name, and day, and only 2 levels for everything else. This yields $P = 432$.

```{r}
include_graphics("../notes/figures/el_salvador/time_table_small_P.png")
```

```{r}
include_graphics("../notes/figures/el_salvador/overlap_distribution_smallP.png")
```

```{r}
include_graphics("../notes/figures/el_salvador/m_posterior_smallP.png")
```

## Limitation of parlr

Doing this analysis made me realize a limitation of this `parlr` method. When you have many many fields and levels, you can have situations where $P > n_A$, which means that doing calculations over all possible patterns will actually be slower than the standard method. Of course, there will only be at most $n_A$ realized patterns (and probably less than that ), but computational saving will only be significant when $P << n_A$.

One other issue regarding the size of $P$: Numerically, missing values lead to another unique pattern. Consider the previous examples with 5 fields with only 2 agreement levels, yeilding $P = 2^5 =32$ unique patterns. If there is at even one missing value for each of the fields, this would lead to $P = 3^5 =243$ unique patterns. For large $n_A$ this is still a big savings, but its important to note how quickly $P$ can grow, especially with regards to missing values.

(Sadinle's `BRL` incorrectly classifies all missing values as disagreements. Adopting this would help keep $P$ small, but is bad for tons of different reasons.)

@@

I think its nice that it demonstrates the influence of the $P$ patterns, but I'm not sure if that's enough. Let me know your thoughts on this!
